---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# areaofcircle

The goal of areaofcircle is to help users find the area of a circle when they are given its radius. 
The function will only accept a radius value greater than zero. 

## Installation

You can install the development version of areaofcircle from [GitHub](https://github.com/) using the following code:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/areaofcircle")
```

## Example

Below are three examples of the function in use. The second and third examples show the error messages that will be outputted if a character or negative value are entered into the function:
```{r example, error=TRUE}
library(areaofcircle)
#  Find the area of a circle with given radius of 4.
print(area_of_circle(4))
# Run area_of_circle() function to see what happens when a character is inputted.
print(area_of_circle("red"))
# Find area of a circle when given negative radius of -6.
# Note: a radius cannot be -6, I am just trying to show what happens when numeric
# data is inputted that does not fit the conditions of the code.
print(area_of_circle(-3))
```
